NIRCam Calibration Plan

### 2016-12-02 ms.tex
I corrected the optical density of the ND filter.

There are several ways to improve saturation limits:
\begin{itemize}
\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
\item Use a neutral density square in the coronagraph mask. The neutral density filters have an attenuation of around 10$^2.6$ or 6.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region. Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.3 mags
\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\end{itemize}

>>>>

There are several ways to improve saturation limits:
\begin{itemize}
\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
\item Use a neutral density square in the coronagraph mask. The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region. Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.8 mags
\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\end{itemize}
